### 2015-07-06 intro-new.tex
revise intro: section 1.5.1 on TE

This part of the thesis considers network infrastructure of Internet service providers (ISPs), and the task of traffic engineering in these networks. Traffic engineering configures network routing plays a key role in determining the cost and congestion in ISP networks. But, ISP traffic engineering is not isolated from, and interacts with content placement and request redirections decisions made at the application layer. The over-arching goal of our work is to design and evaluate ISP traffic engineering techniques in a content-dominated network while accounting for their interactions with content placement and request redirection.

We address the above question two scenarios. First scenario in more commonly visible in present-day internet, in which an ISP has little control of placement and redirection. Second scenario is motivated by a recent, potentialy transformative trend: Network CDNs -- an ISP that runs a cdn on its infrastructure, and as a result enjoys full control over placement and routing on its network.

@@

We define location diversity as the presence of content at multiple network locations, and the ability of end-users to download content from those locations. Location diversity is enabled by several types of applications and services, such as CDNs, P2P, mirrored websites. We model location diversity using a simple content placement scheme -- randomly placing content at multiple locations --, to reflect the limited control of ISPs on content placement in their networks. We further assume that users can download content in parallel from all locations.

Our work presents an experimental comparison of several classes of TE schemes using data from real ISP topologies and traffic matrices for running large-scale experiments simulating network traffic as a collection of TCP flows. Our key findings are as follows: (1) We find that all traffic engineering schemes, including shortest-path routing, multi-path label switching routing, routing robust to unpredictable variations as well as optimal traffic engineering, achieve similar application performance and network capacity.   (2) We find that even a static shortest-path routing, or in other words no-TE scheme is also 30\% sub-optimal in terms of network capacity. Overall, these results suggest that even a limited placement flexibility reduces the value of sophisticated TE schemes, e.g., optimal TE, over simpler TE schemes, e.g., shortest path routing. These results are further strengthed in the case of a network CDN where the content placement flexibility is even greater.

@@

A growing trend which is growing stronger is that isp's are getting more interested in deploying CDNs on their network.

30+ isps are deploying cdns. CDNs are offering licensed cdn technology.

Additional source of revenue due to content traffic.

Content caching to reduce growth in video traffic.

Potentially a game-changing trend where isps control content delivery in addition to network routing, make all three decisions: placement, redirection, routing.

how should these decisions be made to optimize traffic engineering objectives such as link utilization. as well content delivery objectives such as user-perceived latency.

Addressing these questions forms the motivation of this part of the thesis.

Our work evaluates x, y, z via ...

Our works shows ...

Our works implies ...

A network CDN (NCDN) is an ISP that offers content delivery to users on its network. Indeed, ISPs have shown a great interest in deploying NCDNs to monetize their CDN service and to achieve network traffic reduction due to content caching \cite{telco-cdn-arguments}. Unlike a traditional ISP, an NCDN enjoys full control over placement and routing in their network. Accordingly, our work evaluates several combinations of placement and routing schemes that an NCDN can deploy. First, a simple caching scheme for placement and a static-shortest path routing. Second, a joint optimization of placement and routing based on historic demand patterns. Third,  an ideal joint optimization with future knowledge of content demand.  Of particular interest to NCDNs are demand-oblivious schemes such as the first scheme, as they make placement and routing decisions without measurement of content demand and simplify network management for the operators.

Our key findings, based on real network topologies, and extensive traces from Akamai CDN, demonstrate the effectiveness of a demand-oblivious scheme. First, the demand-oblivious scheme significantly outperforms a scheme that optimizes placement and routing jointly based on historical content demand and performs close to an ideal joint-optimization strategy with knowledge of future content demand.  Second, optimizing routing matters little in NCDNs: whether a static shorted-path routing or a routing optimized based on measured traffic demands is used along with a caching scheme, the network cost differs by less than 10\%.

\textbf{Summary:} Network operators have traditionally focused on optimizing routing to achieve their objectives, but my research shows that in a content-dominated network, they are better served by leveraging placement flexibility using simple demand-oblivious placement schemes.

@@

TODO: explain the adverse effects of poor support for mobility.

@@

\textbf{Auspice name resolution service:} A key component of our naming system is the Auspice: a scalable geo-distributed service for mapping names to network addresses under high mobility. A key decision in Auspice's design is that of placement of name records that store the name-to-address mapping. The placement problem is challenging due to a fundamental cost-vs.-performance trade-off: placing name record at multiple locations improves latency of content accesses but increases update propagation costs. To address this challenge, Auspice name resolution service infers pockets of high demand for a name and uses a heuristic placement strategy that selects both the number and location of the replicas in a demand-aware manner to provide low request latency, low update cost, and high availability.  We extensively evaluate Auspice for an expected workload of a global name service and show that it significantly outperforms both commercial managed DNS services as well as DHT-based replication alternatives to DNS. Auspice is deployable in the Internet today as a scalable managed DNS provider, potentially enhacing support for mobility in the present day Internet as well.

>>>>

Traffic engineering in ISP networks is not isolated from decisions at the application layer.
The primary goal of traffic engineering is to configure network routing to reduce capacity provisiong costs as well as network congestion.
But, in a content dominated network, traffic engineering interacts with content placement and request redirection. The over-arching goal of our work is to design and evaluate ISP traffic engineering techniques while accounting for their interaction with content placement and request redirection.

We address the above question in two scenarios. The first scenario in a more common occurence in present day Internet, in which an ISP has little control over placement and redirection. The second scenario is motivated by a recent, potentialy transformative trend: Network CDNs (NCDNs) -- CDNs deployed by ISPs on their infrastructures. Unlike traditional ISPs, an NCDN enjoys full control over placement, redirection and routing on its network.

@@

We model a content-dominated ISP network by accounting for its content \emph{location diversity} -- the presence of content at multiple network locations, and the ability of end-users to download content from those locations. Location diversity is enabled by several types of applications and services, such as CDNs, P2P, mirrored websites. We create location diversity using a simple content placement scheme -- randomly placing content at multiple locations --, to reflect the limited control of ISPs on content placement in their networks.

%We further assume that users can download content in parallel from all locations.

Our work presents an experimental comparison of several classes of traffic engineering schemes using data from real ISP topologies and traffic matrices. Our key findings are as follows: (1) We find that all traffic engineering schemes, including shortest-path routing, multiprotocol label switching routing, routing that is robust to unpredictable variations as well as optimal traffic engineering, achieve similar application performance and network capacity.   (2) We find that even a static shortest-path routing, or in other words a ``no'' traffic engineering  scheme is at most 30\% sub-optimal in terms of network capacity. Overall, these results suggest that even a limited placement flexibility reduces the value of sophisticated traffic enginering schemes, e.g., optimal traffic engineering, over simpler traffic engineering schemes, e.g., shortest path routing. These results are further strengthed in the case of a network CDN where the content placement flexibility is even greater.

@@

There are strong economic factors motivating ISPs to transform into network CDNs for delivering content to users on its network: falling bandwidth prices due to competition and technology trends, potential sources of revenue by selling content-based services to end-users, easy availability of CDN technology in the form of licensed and managed CDNs and reduction in backbone traffic due to content caching via NCDNs are some of the most prominent factors \cite{telco-cdn-arguments}. Today, more than 30 ISPs have deployed NCDNs.

NCDNs represent a paradigm shift in which both content delivery and traffic engineering is handled by a single entity. 
A natural question is to ask how should NCDNs handle placement, redirection and routing for optimize traffic engineering objectives such as maximum link utilization, as well content delivery objectives such as user-perceived latency. Accordingly, our work evaluates several combinations of placement and routing schemes that an NCDN can deploy. First, a simple caching scheme for placement and a static-shortest path routing. Second, a joint optimization of placement and routing based on historic demand patterns. Third,  an ideal joint optimization with future knowledge of content demand.  Of particular interest to NCDNs are demand-oblivious schemes such as the first scheme, as they make placement and routing decisions without measurement of content demand and simplify network management for the operators.

Our key findings, based on real network topologies, and extensive traces from Akamai CDN, demonstrate the effectiveness of a demand-oblivious scheme. First, due to poor predictability of content demand and the churn in content workloads, a scheme that optimizes placement, redirection and routing jointly based on historical content demand performs much worse than the simple demand-oblivious scheme. Second, the demand-oblivious scheme performs close to an ideal joint-optimization strategy with knowledge of future content demand, largely because the caching scheme achieves high cache hit rates from caches placed inside the network.  Third, optimizing routing matters little in NCDNs: whether a static shorted-path routing or a routing optimized based on measured traffic demands is used along with a caching scheme, the network cost differs by less than 10\%.

\textbf{Summary:} ISPs have traditionally focused on optimizing routing to achieve their objectives, but our research shows that in a content-dominated network, they are better served by leveraging placement flexibility using simple placement schemes.

@@

Internet's poor support for mobility is visible at several corners:

@@

\textbf{Auspice name resolution service:} A key component of our naming system is Auspice: a scalable geo-distributed service for mapping names to network addresses under high mobility. A key decision in Auspice's design is that of placement of name records that store the name-to-address mapping. The placement problem is challenging due to a fundamental cost-vs.-performance trade-off: placing name record at multiple locations improves latency of content accesses but increases update propagation costs. To address this challenge, Auspice name resolution service infers pockets of high demand for a name and uses a heuristic placement strategy that selects both the number and location of the replicas in a demand-aware manner to provide low request latency, low update cost, and high availability.  We extensively evaluate Auspice for an expected workload of a global name service and show that it significantly outperforms both commercial managed DNS services as well as DHT-based replication alternatives to DNS. Auspice is deployable in the Internet today as a scalable managed DNS provider, potentially enhacing support for mobility in the present day Internet as well.
